### 2020-12-18 09_discussion.tex
Updates from Overleaf
changes

The current work demonstrates the underlying structure of synchronized dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions. Existing efficient solvers for reductions of the dual-arm problem made \algo effective. 
\cameraready
{
Future work will attempt to explore the $k-$arm case. The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions. Regrasp reasoning can extend this work to non-monotone problem instances. The incorporation of manipulation and grasp reasoning can apply such solvers to more cluttered environments.
}

>>>>

The current work demonstrates the underlying structure of synchronized \dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions. Existing efficient solvers for reductions of the dual-arm problem made \algo effective.

\cameraready
{
Work beyond the methods presented in this paper has explored the $k-$arm case. The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions. Effective approximate or lazy solutions to the $k-$arm case can also prove to be power heuristics to the general multi-arm task planning~\cite{shome2019multiarm} challenge. Regrasp reasoning and the use of intermediate locations can extend this work to non-monotone problem instances. The incorporation of manipulation and grasp reasoning with \revisions{real-world object geometries} can also extend such solvers to more cluttered environments. This work serves as a stepping stone in building towards these rich problem domains.
}

### 2020-12-18 biography.tex
changes

%\begin{wrapfigure}{l}{0.25\textwidth}
%\begin{center}
%\includegraphics[width=0.24\textwidth]{figures/biography/rahul_shome.jpeg}
%\end{center}
%\end{wrapfigure} \par 
\vspace{0.3in}
\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/rahul_shome.jpeg}}
\noindent {\bf Rahul Shome} is pursuing his Ph.D. in Computer
Science at Rutgers University. He has been working with Prof. Kostas Bekris at
the PRACSYS Lab. His research interests include multi-robot motion
planning, manipulation planning, warehouse automation, and problems in rearrangement task planning.

>>>>

%\begin{wrapfigure}{l}{0.25\textwidth}
%\begin{center}
%\includegraphics[width=0.24\textwidth]{figures/biography/rahul_shome.jpeg}
%\end{center}
%\end{wrapfigure} \par 
\vspace{0.3in}
\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/rahul_shome.jpeg}}
\noindent {\bf Rahul Shome} is a Postdoctoral Research Associate at Kavraki Lab, Rice University, working with Prof. Lydia Kavraki. He attained his Ph.D. in Computer Science from Rutgers University where he worked with Prof. Kostas Bekris at the PRACSYS Lab. His research interests include motion
planning, manipulation, and task-and-motion planning with a special focus on practical real-world robotic solutions with strong theoretical guarantees.
